Usability of Modern Display Technologies

### 2014-10-16 mental-model-paper/paper2.tex
more background work/methods work

\section{Background/ Prior Work/ Literary Review}
\subsection{Limitations/Proposed Solutions}
There exists a fair amount of previous work pertaining to the the limitations of touch sensitive screens. One limitation that is discussed in the literature is how typing on flat surfaces---with no physical keys to guide the fingers---requires heightened visual attention. A study by Hussain Tinwala and Scott MacKenzie suggests that since the visual demand on the user is increased, concentration is diverted from the thoughts being expressed. \cite{Tinwala:2010:ETE:1868914.1868972} The lack of tactile features not only diverts attention from thoughts being expressed, but moreover, it makes the devices extremely difficult to use for Individuals with Blindness or Severe Visual Impairment (IBSVI). A study from Virginia Polytechnic Institute and State University examined how, even with the use of \textit{VoiceOver}\footnote{\textit{VoiceOver} for OS X tells users what is on the screen and walks users through actions.\cite{VoiceOver}} functionality, touch screens do not provide sufficient support for IBSVI. These users are only able to ``develop a spatial mental model for the interface or the screen through dead reckoning" as there is an ``absence of any landmark other than the boundary of the device." \cite{El-Glaly:2013:TTF:2460625.2460665}

@@

\section{Methods}
There exist several input entry methods, however, that attempt to address this problem. For instance, Tinwala and MacKenzie present a system that includes auditory and tactile feedback to guide eyes-free entry using speech and non-speech sounds. \cite{Tinwala:2010:ETE:1868914.1868972} 
Another proposed solution comes from Tactus Technology, a company in Fremont, California. Employees from Tactus Technology are creating a keyboard with shape-shifting keys that pop up from the screen's surface when needed and recede again when no longer necessary.\cite{Tactus} Craig Ciesla, the co-founder of the company, said that the keyboard will be offered later this year.

>>>>

\section{Background/ Prior Work/ Literary Review}
\subsection{Limitations/Proposed Solutions}
There exists a fair amount of previous work pertaining to the usability of touch sensitive screens. The literature often articulates limitations, as well as proposed solutions, with respect to usability. One limitation that is discussed in the literature is how typing on flat surfaces---with no physical keys to guide the fingers---requires heightened visual attention. A study by Hussain Tinwala and Scott MacKenzie suggests that since the visual demand on the user is increased, concentration is diverted from the thoughts being expressed. \cite{Tinwala:2010:ETE:1868914.1868972} The lack of tactile features not only diverts attention from thoughts being expressed, but moreover, it makes the devices difficult to use for Individuals with Blindness or Severe Visual Impairment (IBSVI). A study from Virginia Polytechnic Institute and State University examined how, even with the use of features such as  \textit{VoiceOver}\footnote{\textit{VoiceOver} for OS X tells users what is on the screen and walks users through actions.\cite{VoiceOver}}, touch screens still do not provide sufficient support for IBSVI. These users are only able to ``develop a spatial mental model for the interface or the screen through dead reckoning" as there is an ``absence of any landmark other than the boundary of the device." \cite{El-Glaly:2013:TTF:2460625.2460665}

@@

\section{Methods}
The prior work in the field demonstrates how there is a variety of different advantages as well as limitations that can be examined when evaluating the usability of touchscreen devices. This study will focus exclusively on the limitation of the minimal tactile feedback provided by touchscreen devices, and what this means with respect to usability.

There exist several input entry methods, however, that attempt to address this problem. For instance, Tinwala and MacKenzie present a system that includes auditory and tactile feedback to guide eyes-free entry using speech and non-speech sounds. \cite{Tinwala:2010:ETE:1868914.1868972} 
Another proposed solution comes from Tactus Technology, a company in Fremont, California. Employees from Tactus Technology are creating a keyboard with shape-shifting keys that pop up from the screen's surface when needed and recede again when no longer necessary.\cite{Tactus} Craig Ciesla, the co-founder of the company, said that the keyboard will be offered later this year.
